Assessing the Impact of Vision Zero on Traffic Collisions in Toronto Neighborhoods (2014–2021):

### 2024-12-04 paper/paper.qmd
Readme Done Minor Changes made to the quarto document

   - **Data Access**: [Toronto Traffic Collisions Data](https://www.toronto.ca/city-government/data-research-maps/open-data/open-data-catalogue/)

@@

# Save cleaned data
write_csv(collisions_clean, here("data", "analysis_data", "collisions_clean.csv"))
```
## **Descriptive Analysis and Visualizations**

@@

$Y_{it} \sim \text{NegBin}(\mu_{it}, \theta)$

@@

$\log(\mu_{it}) = \beta_0 + \beta_1 \text{Year}_t + \beta_2 \text{PostVisionZero}_t + \beta_3 \text{Neighborhood}_i + \beta_4 \text{InjuryRate}_{it} + \beta_5 \text{FatalityRate}_{it}$

@@

   $\text{InjuryRate}_{it} = \frac{\text{injuries}_{it}}{\text{total\_collisions}_{it}}$

   $\text{FatalityRate}_{it} = \frac{\text{fatalities}_{it}}{\text{total\_collisions}_{it}}$

@@

```{r residual-plot, fig.cap="Figure 1: Residuals vs. Fitted Values"}
#| echo: false
# Plot residuals vs. fitted values
residuals <- residuals(nb_model, type = "pearson")
fitted_values <- fitted(nb_model)

>>>>

   - **Data Access**: [Toronto Traffic Collisions Data](https://open.toronto.ca/dataset/police-annual-statistical-report-traffic-collisions/)

@@

# Save cleaned data
write_csv(collisions_clean, here("data", "analysis_data", "collisions_clean.csv"))
```

## **Descriptive Analysis and Visualizations**

@@

\[$Y_{it} \sim \text{NegBin}(\mu_{it}, \theta)$\]

@@

\[$\log(\mu_{it}) = \beta_0 + \beta_1 \text{Year}_t + \beta_2 \text{PostVisionZero}_t + \beta_3 \text{Neighborhood}_i + \beta_4 \text{InjuryRate}_{it} + \beta_5 \text{FatalityRate}_{it}$\]

@@

\[$\text{InjuryRate}_{it} = \frac{\text{injuries}_{it}}{\text{total\_collisions}_{it}}$\]

\[$\text{FatalityRate}_{it} = \frac{\text{fatalities}_{it}}{\text{total\_collisions}_{it}}$\]

@@

```{r residual-plot, fig.cap="Residuals vs. Fitted Values"}
#| echo: false
# Plot residuals vs. fitted values
residuals <- residuals(nb_model, type = "pearson")
fitted_values <- fitted(nb_model)
